---
title: "HW6"
format: pdf
highlight-style: tango
editor: visual
execute:
  echo: false
fig-width: 6.5
fig-height: 8.0
bibliography: hw_6.bib
---

## Imports
```{r}
#| warning: false
library(readr)
library(here) 
library(rio) 
library(tidyverse)
library(knitr) 
library(ggplot2)

```
## Commit 1

```{r}
star <- import(here("data","star.csv"))  
```

## Commit 2

This is an example of an in-text citation where the we cite Brown [-@brown1999] but only include the author's year of publication in the parenthesis. Here is another example where using the work of @amelink2009. Meanwhile, this is another example where the author and year is included both in the parenthetical citations [@hyde1990]. We can also refer to this statement to illustrate BibTex citation in Quarto [@felson1991].

## Commit 3
```{r}
#| message: false
star %>%   
  group_by(sex,frl) %>%  
  summarise(mean(tmathss), sd(tmathss),   
            mean(treadss), sd(treadss)) %>%  
  kable(col.names = c("sex","frl","math_mean", "math_sd", "rdg_mean", "rdg_sd"), 
        digits = 3,booktabs = TRUE) 
```

## Commit 4
```{r}
#| message: false
star %>%
  ggplot(aes(x = totexp, y = tmathss)) +
  geom_point(color = "gray60") +
  geom_smooth(aes(color = frl), method = lm) +
  scale_color_discrete(labels = c("Free/Reduced Price Meals", "Paid Meals"))+
  labs(x = 'Teacher Experience (years)',
       y = 'Total Math Scale Score',
       title = 'Relation between teacher experience and math scores',
       subtitle = 'Separate regression lines displayed by free/reduced price lunch status',
       color = "Lunch Status")+
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.justification = "center")
  
```
# References